Title Goes Here

### 2020-04-28 analysis/paper/paper.Rmd
fix namespace clash

library(dplyr)
SYG1_2df_sitename <- SYG1_2df %>% 
  mutate (files = str_remove_all(files, "_\\d+.tps")) %>% 
  rename(sitename = files)

@@

library(dplyr)
SYG1_1df_sitename <- SYG1_1df %>% 
  mutate (files = str_remove_all(files, "_\\d+.tps")) %>% 
  rename(sitename = files)

>>>>

library(dplyr)
SYG1_2df_sitename <- SYG1_2df %>% 
  mutate (files = str_remove_all(files, "_\\d+.tps")) %>% 
  dplyr::rename(sitename = files)

@@

library(dplyr)
SYG1_1df_sitename <- SYG1_1df %>% 
  mutate (files = str_remove_all(files, "_\\d+.tps")) %>% 
  dplyr::rename(sitename = files)
